Hydras, Ordinals \& Co. \\ A library in Coq of entertaining formal mathematics

### 2021-09-25 doc/JFLA2022/paper.tex
fix typos
small correction

\TODO[Pierre]{
Using the equations for $H'$ as rewrite rules, we could ``compute'' the number of rounds of the battle starting with the hydra of Figure~\ref{fig:start} and $0$ as initial step. this number has
at least $2^{10^{21}}$ binary digits. Obtaining this result is an interesting example of relationship between proof and computation.}

>>>>

\TODO[Pierre]{
  Using the equations of $H'$ as rewrite rules, we studied the
  number of steps  of the battle starting with the hydra of Figure~\ref{fig:start} and $0$ as initial step. This number has
at least $2^{10^{21}}$ binary digits. Obtaining this result is an interesting example of relationship between proof and computation.}
